\section{Main Theorem and Foundational Consequence}\label{sec:main-theorem}

The preceding sections now provide the full chain of argument. \Cref{thm:no-internal-totalization} blocks direct enlargement of old primitive graphs on old tuples. \Cref{thm:auxiliary-dichotomy} classifies purported operators by the status of their load-bearing auxiliary data. \Cref{thm:exhaustion-theorem} and Proposition~\ref{prop:five-disposition} show that the standard apparent strengthening mechanisms are exhausted and disposed of. \Cref{thm:case-study-closure} shows that the same dichotomy governs the flagship families. \Cref{thm:no-emergent-family} then closes the interaction loophole. What remains is to state the resulting theorem in one place.

\begin{theorem}[No new internal operator power on a fixed base]\label{thm:main-no-new-power}
Let $\B=(X,\Omega,\A)$ be a nondegenerate base structure. Let $F$ be a purported carrier-preserving operator on $\B$ belonging to the interaction-generated closure of the strengthening mechanisms classified in \Cref{sec:exhaustion,sec:no-emergence}. Then exactly one of the following holds.
\begin{enumerate}[label=(\alph*)]
    \item $F$ acts conservatively on the old-base-relevant content of $\B$.
    \item $F$ depends essentially on external parameters, witnesses, evaluators, or ambient enlargement and is therefore not internal to $\B$.
\end{enumerate}
Consequently:
\begin{enumerate}[label=(\roman*)]
    \item no such operator totalizes a genuinely partial old primitive on old tuples;
    \item no composition, iteration, diagonal packaging, or representation change among the classified families yields a new carrier-preserving source of admissible operator power on the original base.
\end{enumerate}
\end{theorem}

\begin{proof}
By \Cref{thm:exhaustion-theorem}, every apparent internal strengthening of the fixed base falls under one of the mechanisms in \Cref{def:five-mechanisms}. Proposition~\ref{prop:five-disposition} shows that each such mechanism is either blocked or else reveals that no genuine internal strengthening has occurred. \Cref{thm:case-study-closure} applies that classification to the flagship mathematical families treated in \Cref{sec:case-studies}. Finally, \Cref{thm:no-emergent-family} shows that the same classification is stable under the natural interaction operations by which those families might be recombined.

Clause (a) collects the conservative cases, and clause (b) collects the externally dependent cases. The first consequence is just the rigidity result \Cref{thm:no-internal-totalization} carried through the later sections. The second consequence is the content of \Cref{thm:no-emergent-family}. No third possibility remains.
\end{proof}

\begin{corollary}[No internal re-entry principle]\label{cor:no-internal-reentry-principle}
External methods may establish theorems, transfer principles, canonical readbacks, and invariance claims about a fixed base. What they do not do is return as new internal operator power on that base unless the return map is conservative on old-base-relevant content.
\end{corollary}

\begin{proof}
Immediate from \Cref{thm:main-no-new-power,cor:no-reentry}.
\end{proof}

\subsection*{Foundational consequence}

The intended consequence is therefore exact rather than rhetorical. The paper does not say that external methods are dispensable, or that their outputs are merely verbal, or that all mathematically important distinctions collapse to definitional equivalence. It says something narrower and, for that reason, more defensible. Once a base structure and its admissibility regime are held fixed, there is no additional internal operator power to be extracted from those methods except by conservative readback.

That conclusion supports a foundational ``no internal re-entry'' principle. Completions, monster models, forcing extensions, universal-property arguments, and other ambient methods remain legitimate and often indispensable. They can reveal structure, establish invariance, prove existence, and reorganize mathematical understanding. But when their conclusions are transported back to the original base, the fixed-base status of that transport is exhausted by the two cases isolated above: either the transport is conservative on the old base, or else it still depends on the ambient extension and is not an internal operator on the original base.
