\section{Scope and non-claims}
\label{sec:nonclaims}

\subsection{What the manuscript has established}

On the fixed downstream substrate and within the standing conditional of
Section~\ref{sec:targetclass}, the manuscript has established the following.
\begin{enumerate}
    \item a gate-governed fixed-domain definition of admissible reference assignment;
    \item a measurement-reference quotient theorem identifying the unique standing-bearing content
    space for admissible reference assignments;
    \item a corollary that confirmational-role divergence is quotient-relevant rather than semantic skin;
    \item an Everettian non-selection theorem for the bare unitary, entangling, decohering package;
    \item a confirmation criterion tying theory-level confirmation to invariance on the fixed
    measurement-reference quotient;
    \item a fixation-commutation necessity theorem for theory-level confirmation;
    \item a toy witness showing hypothesis-order reversal under divergent admissible assignments;
    \item a lineage theorem showing that memory, anticipation, deliberation, and confirmation share
    one identity-preserving referential dependence; and
    \item a structural exhaustion theorem locating every interpretation package at exactly one locus of
    singular-reference fixing, if it fixes singular reference at all.
\end{enumerate}

\subsection{What the manuscript does not claim}

The manuscript does \emph{not} claim any of the following.
\begin{enumerate}
    \item It does not derive the Born rule, the Hilbert-space formalism, or any specific quantum
    probability law.
    \item It does not prove that Everettian physics is false. It proves only that the bare Everettian
    package is physically non-selective with respect to the target discourse.
    \item It does not settle every metaphysical question in quantum foundations. The taxonomy is
    structural, not a total ranking of interpretations by all virtues.
    \item It does not deny branch-local determinacy. It denies only that branch-local determinacy by
    itself fixes diachronic reference on the target scope.
    \item It does not claim that every scientific use of quantum theory collapses if reference is
    underfixed. Its stronger conclusion is restricted to the discourse named in the standing
    conditional: memory, anticipation, deliberation, and theory-level confirmation through
    measurement records.
    \item It does not treat semantic infrastructure constraints as extra dynamical laws or hidden
    variables. They remain restrictions on admissible reference assignments imposed by the
    explanatory work the theory is asked to do.
    \item It does not deny the coherence of discourse-deflationary responses. It says only that they
    refuse the target explanatory burden rather than satisfy it.
\end{enumerate}

\subsection{Role of these limits}

These limits keep the target of the paper exact. The manuscript is a fixed-domain quotient-and-
uniqueness paper about measurement-record discourse in physically non-selective theories. Its aim is
not to settle every question in quantum foundations, but to isolate the referential condition under
which measurement records can function as theory-level evidence at all.
