\section{Appendix: companion structural package and exact imports}
\label{app:later-architecture}

This appendix states exactly which companion results are used as fixed-domain background and how
they are used. The point is transparency, not retrospective promotion. The present manuscript is
conditional on these results; they are not hidden premises.

\subsection{Imported fixed-domain package}

The main body uses the following companion results only at the level stated below.
\begin{enumerate}
    \item \textbf{Kernel closure and non-derivability.} Admissibility, standing, reference, and
    irreversibility are forced for the target class of non-degenerate reasoning, and there is no
    faithful same-scope lower generator.
    \item \textbf{AMetric boundary and gate uniqueness.} There is no admissibility-relevant
    parameterization, selector, ranking, or same-scope competing gate on the fixed scope.
    \item \textbf{Standing conservation.} There are no same-scope repairs, generators, or primitive
    carriers, and no transfer without fresh target gating.
    \item \textbf{Unique admissible interior.} The admissible interior is unique up to lawful
    equivalence.
    \item \textbf{Trajectory closure.} Same-scope standing failure is irrecoverable under admissible
    continuation.
    \item \textbf{No second invariant / no fourth role.} Any second same-scope invariant collapses to
    bookkeeping or scope change, and any admissibility-preserving role classification factors
    through anchor/tensor/skin up to role isomorphism.
\end{enumerate}
The relevant companion manuscripts are
\citep{maley_foundational2026,maley_necessity2026,maley_trajectory2026,maley_unus2026,
maley_clausura2026,maley_ats2026,maley_ametric2026,maley_structura2026}.

\subsection{How those imports are used here}

The imported package is used in exactly four places.
\begin{enumerate}
    \item In Section~\ref{sec:targetclass}, it fixes the downstream substrate and blocks the
    \enquote{your framework is optional} objection.
    \item In Section~\ref{sec:semanticcore}, it forces soundness of measurement-reference
    presentations and therefore yields quotient uniqueness on the fixed scope.
    \item In Section~\ref{sec:confirmation}, it turns confirmational divergence into a standing-bearing
    difference rather than a mere semantic redescription.
    \item In Section~\ref{sec:taxonomy}, it closes the no-fifth-locus theorem by ruling out a second
    same-scope admissibility classifier, a second invariant, or a fourth admissibility-bearing role.
\end{enumerate}
No proof in the main body uses the companion papers for anything stronger than these fixed-domain
constraints.

\subsection{What the present paper adds beyond the companion package}

The companion papers do not by themselves solve the measurement problem. What the present paper
adds is a fixed-domain quotient-and-uniqueness analysis of measurement-record discourse in
physically non-selective theories. Its distinctive results are:
\begin{enumerate}
    \item the explicit admissible assignment space for diachronic measurement-record discourse;
    \item the measurement-reference quotient theorem;
    \item the Everettian non-selection theorem in this measurement-specific setting;
    \item the fixation-commutation criterion for theory-level confirmation; and
    \item the common-lineage theorem for confirmation, memory, anticipation, and deliberation.
\end{enumerate}
So the relation between the present paper and the companion corpus is asymmetric. The companion
results fix the downstream substrate; the present paper applies that substrate to measurement-record
reference.
