\begin{thebibliography}{99}

\bibitem[Einstein et~al.(1935)Einstein, Podolsky, and Rosen]{epr1935}
Albert Einstein, Boris Podolsky, and Nathan Rosen.
\newblock Can quantum-mechanical description of physical reality be considered complete?
\newblock \emph{Physical Review}, 47(10):777--780, 1935.

\bibitem[Bell(1964)]{bell1964}
J.~S. Bell.
\newblock On the {Einstein Podolsky Rosen} paradox.
\newblock \emph{Physics Physique Fizika}, 1(3):195--200, 1964.

\bibitem[Everett(1957)]{everett1957}
Hugh Everett~III.
\newblock ``Relative state'' formulation of quantum mechanics.
\newblock \emph{Reviews of Modern Physics}, 29(3):454--462, 1957.

\bibitem[Zurek(2003)]{zurek2003}
Wojciech~H. Zurek.
\newblock Decoherence, einselection, and the quantum origins of the classical.
\newblock \emph{Reviews of Modern Physics}, 75(3):715--775, 2003.

\bibitem[Schlosshauer(2005)]{schlosshauer2005}
Maximilian Schlosshauer.
\newblock Decoherence, the measurement problem, and interpretations of quantum mechanics.
\newblock \emph{Reviews of Modern Physics}, 76(4):1267--1305, 2005.

\bibitem[Deutsch(1999)]{deutsch1999}
David Deutsch.
\newblock Quantum theory of probability and decisions.
\newblock \emph{Proceedings of the Royal Society A}, 455(1988):3129--3137, 1999.

\bibitem[Greaves(2004)]{greaves2004}
Hilary Greaves.
\newblock Understanding {Deutsch}'s probability in a deterministic multiverse.
\newblock \emph{Studies in History and Philosophy of Modern Physics}, 35(3):423--456, 2004.

\bibitem[Lewis(1979)]{lewis1979}
David Lewis.
\newblock Attitudes de dicto and de se.
\newblock \emph{The Philosophical Review}, 88(4):513--543, 1979.

\bibitem[Sebens and Carroll(2018)]{sebenscarroll2018}
Charles~T. Sebens and Sean~M. Carroll.
\newblock Self-locating uncertainty and the origin of probability in {Everettian} quantum mechanics.
\newblock \emph{The British Journal for the Philosophy of Science}, 69(1):25--74, 2018.

\bibitem[Wallace(2012)]{wallace2012}
David Wallace.
\newblock \emph{The Emergent Multiverse: Quantum Theory according to the Everett Interpretation}.
\newblock Oxford University Press, Oxford, 2012.

\bibitem[Ghirardi et~al.(1986)Ghirardi, Rimini, and Weber]{grw1986}
GianCarlo Ghirardi, Alberto Rimini, and Tullio Weber.
\newblock Unified dynamics for microscopic and macroscopic systems.
\newblock \emph{Physical Review D}, 34(2):470--491, 1986.

\bibitem[Bohm(1952a)]{bohm1952}
David Bohm.
\newblock A suggested interpretation of the quantum theory in terms of ``hidden'' variables. {I}.
\newblock \emph{Physical Review}, 85(2):166--179, 1952.

\bibitem[Bohm(1952b)]{bohm1952b}
David Bohm.
\newblock A suggested interpretation of the quantum theory in terms of ``hidden'' variables. {II}.
\newblock \emph{Physical Review}, 85(2):180--193, 1952.

\bibitem[Fuchs et~al.(2014)Fuchs, Mermin, and Schack]{fuchs2014}
Christopher~A. Fuchs, N.~David Mermin, and R{\"u}diger Schack.
\newblock An introduction to {QBism} with an application to the locality of quantum mechanics.
\newblock \emph{American Journal of Physics}, 82(8):749--754, 2014.

\bibitem[Rovelli(1996)]{rovelli1996}
Carlo Rovelli.
\newblock Relational quantum mechanics.
\newblock \emph{International Journal of Theoretical Physics}, 35(8):1637--1678, 1996.

\bibitem[Maley(2026a)]{maley_foundational2026}
Amos Jay Maley.
\newblock \emph{Foundational Closure of Admissibility and Standing: Non-Derivability, Minimality, and the Kernel of Non-Degenerate Reasoning}.
\newblock Companion manuscript, 2026.

\bibitem[Maley(2026b)]{maley_necessity2026}
Amos Jay Maley.
\newblock \emph{Necessity of Admissibility in Non-Degenerate Compositional Systems: AMetric Boundary, Bivalence, and the Unique Admissible Interior}.
\newblock Companion manuscript, 2026.

\bibitem[Maley(2026c)]{maley_trajectory2026}
Amos Jay Maley.
\newblock \emph{The Mathematics of Coherent Reasoning: A Bivalent Trajectory Theory}.
\newblock Companion manuscript, 2026.

\bibitem[Maley(2026d)]{maley_unus2026}
Amos Jay Maley.
\newblock \emph{Unus Solus Possibilis Est: Corpus Closure and Uniqueness of the Admissible Interior}.
\newblock Companion manuscript, 2026.

\bibitem[Maley(2026e)]{maley_clausura2026}
Amos Jay Maley.
\newblock \emph{Clausura Ex Necessitate Structurae: Closure from the Necessity of Structure}.
\newblock Companion manuscript, 2026.

\bibitem[Maley(2026f)]{maley_ats2026}
Amos Jay Maley.
\newblock \emph{Anchor / Tensor / Skin: A Role Decomposition for Admissible Description}.
\newblock Companion manuscript, 2026.

\bibitem[Maley(2026g)]{maley_ametric2026}
Amos Jay Maley.
\newblock \emph{The AMetric Boundary: Necessity, Non-Parameterization, and Closure by Exhaustion}.
\newblock Companion manuscript, 2026.

\bibitem[Maley(2026h)]{maley_structura2026}
Amos Jay Maley.
\newblock \emph{Structura Ex Necessitate Standardis Modelis: A Standalone Forced-Derivation Ledger for Standard-Model Bookkeeping under Admissible Redescription and Transport Closure}.
\newblock Companion manuscript, 2026.

\end{thebibliography}
