\section*{Archive transcription of the December 2025 source note}

\noindent\textbf{Title:} \emph{The Measurement Problem as a Problem of Reference}.\\
\textbf{Author:} Amos Jay Maley.\\
\textbf{Date:} December 2025.

\medskip

This archive file is an editable reconstruction of the source note based on the supplied PDF. It is included so the project contains both the present manuscript materials and a textual record of the original note.

\subsection*{Abstract (transcribed)}

The measurement problem in quantum mechanics is traditionally formulated as a problem concerning outcome definiteness, probability, or state reduction. In this paper, I argue that these formulations presuppose a more fundamental unresolved issue: the determinacy of reference for measurement records in physically non-selective theories. In Everettian quantum mechanics, unitary evolution and decoherence yield multiple branch-histories containing equally valid physical records of measurement outcomes, but provide no principle for selecting which such history is the referent of an observer's diachronic experience. As a result, statements involving memory, anticipation, and agency lack determinate truth conditions unless additional constraints are imposed.

Building on a general framework of semantic infrastructure constraints, I show that the measurement problem is best understood as a problem of reference stabilization rather than of physical outcome selection. Decoherence, while essential for explaining the emergence and stability of quasi-classical structure, is insufficient to fix experiential reference. Collapse theories and hidden-variable models resolve the problem by introducing physical selectors, whereas Everettian approaches require non-dynamical constraints on admissible reference relations. Recognizing this distinction clarifies the logical structure of the measurement problem and explains the persistence of interpretive disagreement in quantum foundations.

\subsection*{Body note}

The complete reconstructed source note can be extended further if a fuller archival transcription is desired. The critical source content has already been incorporated into the present manuscript.
