{\small
\begin{thebibliography}{99}

\bibitem[Barrett and Halvorson(2016)]{BarrettHalvorson2016}
Thomas William Barrett and Hans Halvorson.
\newblock Morita equivalence.
\newblock \emph{The Review of Symbolic Logic}, 9(3):556--582, 2016.

\bibitem[Barwise(1975)]{Barwise1975}
Jon Barwise.
\newblock \emph{Admissible Sets and Structures}.
\newblock Perspectives in Mathematical Logic. Springer-Verlag, Berlin, 1975.

\bibitem[Burmeister(1986)]{Burmeister1986}
Peter Burmeister.
\newblock \emph{A Model Theoretic Oriented Approach to Partial Algebras: Introduction to Theory and Application of Partial Algebras -- Part I}.
\newblock Mathematical Research 32. Akademie-Verlag, Berlin, 1986.

\bibitem[Chang and Keisler(1990)]{ChangKeisler1990}
C.~C. Chang and H.~Jerome Keisler.
\newblock \emph{Model Theory}.
\newblock North-Holland, Amsterdam, third edition, 1990.

\bibitem[Hodges(1993)]{Hodges1993}
Wilfrid Hodges.
\newblock \emph{Model Theory}.
\newblock Encyclopedia of Mathematics and its Applications 42. Cambridge University Press, Cambridge, 1993.

\bibitem[Jech(2003)]{Jech2003}
Thomas Jech.
\newblock \emph{Set Theory: The Third Millennium Edition, Revised and Expanded}.
\newblock Springer Monographs in Mathematics. Springer, Berlin, 2003.

\bibitem[Kanamori(2008)]{Kanamori2008}
Akihiro Kanamori.
\newblock The mathematical development of set theory from {Cantor} to {Cohen}.
\newblock \emph{The Bulletin of Symbolic Logic}, 14(1):1--71, 2008.

\bibitem[Mac Lane(1998)]{MacLane1998}
Saunders Mac Lane.
\newblock \emph{Categories for the Working Mathematician}.
\newblock Graduate Texts in Mathematics 5. Springer, New York, second edition, 1998.

\bibitem[Marker(2002)]{Marker2002}
David Marker.
\newblock \emph{Model Theory: An Introduction}.
\newblock Graduate Texts in Mathematics 217. Springer, New York, 2002.

\bibitem[Simpson(2009)]{Simpson2009}
Stephen~G. Simpson.
\newblock \emph{Subsystems of Second Order Arithmetic}.
\newblock Perspectives in Logic. Cambridge University Press, Cambridge, second edition, 2009.

\end{thebibliography}

}\normalsize
